An Empirical Analysis of the Internet Engineering Task Force with Computational Methods

### 2024-10-06 paper.tex
Figure and Table placement and formatting; tweaks to text

\begin{figure}
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/imc-2021/documents/day_counts_yearly.pdf}
  \caption{
    Days from first draft to RFC publication
  }
  \label{fig:rfcs_days_to_pub}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/imc-2021/documents/draft_counts_yearly.pdf}
  \caption{
    Number of drafts per RFC
  }
  \label{fig:drafts_year}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/imc-2021/documents/page_counts_yearly_dt.pdf}
  \caption{
    RFC page counts
  }
  \label{fig:pages_year}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/imc-2021/documents/update_obsolete_yearly_pct.pdf}
  \caption{
    RFCs that update or obsolete previous RFCs
  }
  \label{fig:updates_year}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/imc-2021/documents/cite_counts_yearly.pdf}
  \caption{
    Number of citations to other Internet-Drafts and RFCs per RFC in each
    year.
  }
  \label{fig:citations_year}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/imc-2021/documents/keyword_usage_rate.pdf}
  \caption{
    Number of occurrences of normative language keywords per page in RFCs
    in each year.
  }
  \label{fig:keyword_usage_rates}
\end{figure}

@@

\input{tables-prev/tma-2023/top-rfcs-errata.tex}
\input{tables-prev/tma-2023/errata-stats-area.tex}

@@

%..................................................................................................
\pb{Errata per RFC Area, Status, and Stream:}
Figure~\ref{fig:errata_per_rfc} shows a CDF of the number of errata filed,
per RFC, in each IETF area. Non-IETF RFCs, e.g., IRTF and independent stream
RFCs, and legacy IETF RFCs, are labelled as ``None''.  We confirm errata in
standards are common: of the 4,373 standards-track RFCs in our dataset,
32.7\% have attracted at least one erratum filing.  However, there are
three notable outliers:
\begin{enumerate}
  \item RFCs published by the Sub-IP (subip) Area have very few errata,
    with only 5\% of subip RFCs attracting errata filings. This temporary
    area -- established in 2001 and concluded in 2005 -- only published 19
    RFCs, resulting in a far smaller sample than the other areas. For
    comparison, the next smallest area, General (gen), published 39 RFCs.
    \emph{gen} RFCs attract a greater number of errata on average, vs.
    \emph{subip} RFCs, likely due to their broader relevance.

@@

In this section, we look at the authorship of published RFCs to explore
how participation in the IETF has changed over time. We show that the
geographic distribution of RFC authors has shifted over time, with the
proportion of authors from the US decreasing and a corresponding rise in
authors from Europe and China (\S\ref{sec:trends-demographics:geographic}).
We similarly explore shifts in affiliation, showing increasing influence of
Huawei and ongoing shifts in the fortunes of many prominent US and European
technology companies (\S\ref{sec:trends-demographics:affiliation}). The
ongoing influence of Cisco and strong input from academic institutions is
also noted.

@@

\begin{figure}
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/imc-2021/authors/top5_countries_normalised.pdf}
  \caption{
    Authorship countries (normalised)
  }
  \label{fig:author_countries_normalised}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/imc-2021/authors/continents_normalised.pdf}
  \caption{
    Authorship continents (normalised)
  }
  \label{fig:author_continents_normalised}
\end{figure}

@@

To measure influence of participants in the IETF we extend the analysis in
Section \ref{sec:org-dyn:participants} and, for each year, build a social
graph based on the \emph{active community} of participants (nodes) who have
email interactions (edges) with any other participant in the previous five
years.

@@

\begin{figure}
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/icwsm-2022/lineplot_proportion_emailscount_top_percentile.pdf}
  \caption{
    Proportion of emails sent (\%) by participants in each period (with
    95\% confidence interval) according to their betweenness-centrality
    percentile (x-axis).  Y2-axis (purple) shows yearly count of emails.
  }
  \label{fig:emailcount_top_percentile}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/icwsm-2022/lineplot_avg_areas_top_percentile.pdf}
  \caption{
    Mean number of areas participated in (with 95\% confidence interval)
    according to their betweenness-centrality percentile in the x-axis,
    ranked from top (0-10) to bottom percentile (91-100).
  }
  \label{fig:areas_participation_top_percentile}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/icwsm-2022/lineplot_age_top_percentile.pdf}
  \caption{
    Mean participation duration (with 95\% confidence interval) according
    to their betweenness-centrality percentile in the x-axis, ranked from
    top (0-10) to bottom percentile (91-100).
  }
  \label{fig:age_top_percentile}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/icwsm-2022/new_influencers_top10_age_longevityInTop10.pdf}
  \caption{
    Percentage of new influential participants breaking into top 10\%
    influencers (black); the average years of participation before entering
    top 10\% (purple); and minimum \#  years new influencers remain in top
    10\% (with 95\% confidence intervals).
  }
  \label{fig:rate_new_influential_participants}
\end{figure}

@@

Each topic is a distribution over words. For example, a \emph{security}
topic might have high probability for \emph{cypher}, \emph{rsa},
\emph{auth}, and related words. We can also use the model to obtain a
vector for any input text as a sparse distribution over all topics, e.g.,
finding that a text is comprised of 30\% security and 70\% video streaming
topics. With this, we generate a vector for each participant in a given
time period by concatenating all messages sent by that participant in the
period and feeding it into the LDA model. The result can be loosely
interpreted as a distribution of topics on which each participant works.

@@

We next measure the topical diversity of a participant by observing the
entropy of their topic vector, their \emph{topic entropy}, defined as
follows:
\begin{equation}
  \eta = - \sum_{i=1}^{|T|} p_i \log p_i \nonumber
\end{equation}
where $T = [p_1, ..., p_N]$ is a topic vector, which defines a probability
distribution over $N$ topics, each $p_i$ is a probability of the $i$-th
topic and $\sum_i p_i = 1$.

@@

\begin{figure}
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/icwsm-2022/coauthor_affiliation_network/lineplot_non_overlapping_authors_emailnetwork_percentile.pdf}
  \caption{
    Percentage of Top 20\% authors that are not 20\% influencers according
    to their betweenness-centrality (email graph) percentile in the x-axis,
    ranked from  top (0-10) to bottom percentile (91-100).
  }
  \label{fig:non_overlapping_coauthornetwork_authors_emailnetwork}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/icwsm-2022/WG_chair_percentile_CDF_before_after.pdf}
  \caption{
    CDF of the percentile of betweenness-centrality of WG chairs in the
    email and co-authorship graph, one year before and after becoming
    chairs.
  }
  \label{fig:wg_chair_before_after}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/icwsm-2022/coauthor_affiliation_network/2019_affiliations_in_otheryears_coauthor_network.pdf}
  \caption{
    Authors in the most common affiliations of top 20\% authors
    (co-authorship graph) in 2015-2019.
  }
  \label{fig:coauthor_affiliation_network2019_otheryears}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/icwsm-2022/coauthor_affiliation_network/heatmap_2019_top10_affiliation_collaboration.pdf}
  \caption{
    Number of drafts co-authored by top 15 most frequently affiliated
    organisations. We only include the top 20\% authors (co-authorship
    graph) of 2015-2019.
  }
  \label{fig:heatmap_2019_coauthordraft_most_frequent_org}
\end{figure}

@@

For instance, if those in leadership positions send lots of email while
receiving little, this suggests a lack of receptiveness of the leadership
to the suggestions from regular participants, and low confidence of those
regular participants to voice their opinions. In contrast, we hypothesise
that if the IETF operates as outlined in its mission statement, in a more
cooperative manner, then communication between those in different roles
will be more symmetric.

@@

\pb{Impact of Role on Communication Patterns:}
To quantify the effect of being in a leadership position has on network
wide communication, we calculate the proportion of three node temporal
motifs, lasting at most a month, in which each node participates over a
year period. These temporal motifs are counted, categorised into the three
hierarchy levels (regular participant, working group chair, area director)
and then proportions are taken of each temporal motif type.

@@

The larger proportion of those in leadership roles in Inward and Mixed Star
temporal motifs, whilst Outward Star motifs remain similar for all levels,
suggests that those in leadership receive more direct communication. The
higher proportion of Triangle motifs for regular participants suggests
their discussion is more of a group activity, whereas working group chairs
and area directors have a larger proportion of one-on-one conversations.  
We therefore interpret the general communication patterns within the IETF
as a discussion amongst participants interspersed with questions sent to,
and announcements from, the working group chairs and area directors.  This
indicates some collaboration between layers and confidence of some regular
participants' to voice their opinions upwards.

\begin{figure*}[t]
  \centering
  \includegraphics[width=\figureWidthTwoColumn]{figures-prev/icwsm-2024/motif_strata_comparison.png}
  \caption{
    Communication patterns analysed by three edge temporal motifs for RPs,
  }
  \label{fig:motif_proportions}
\end{figure*}

@@

@@

\begin{figure*}[t]
  \centering
  \includegraphics[width=\figureWidthTwoColumn]{figures-prev/icwsm-2024/hierarchy_status_comparison.png}
  \caption{
    Connection between roles and activity for regular participants and
    working group chairs viewed in terms of a) Mobility b) Neighbour
    Mobility c) Philanthropy and d) Community over time.
  }
  \label{fig:mob_tax}
\end{figure*}

@@

@@

\begin{figure*}[t]
  \centering
  \includegraphics[width=\figureWidthTwoColumn]{figures-prev/frontiers/sensitive.pdf}
  \caption{
    Patterns of language use by organizational role. Estimated marginal
    means for the LIWC categories: (A) Politics, (B) Ethnicity, and (C)
    Religion. Error bars show 95% confidence intervals.
  }
  \label{fig:sensitive}
\end{figure*}

@@

@@

\renewcommand{\tabcolsep}{0.5cm}
\begin{table*}
\centering
\begin{tabular}{lcccccccc}
\toprule
                        & \multicolumn{4}{c}{$\neg \mathit{TXT}$}
                        & \multicolumn{4}{c} {$\mathit{TXT}$} \\
\midrule
                       & AUC & F1 & P & R & AUC & F1 & P & R \\
\midrule
Baseline               &  .500 & .445 & .401 & .500  &  .500 & .445 & .401 & .500 \\
\midrule
Comm. patterns         &  .644 & .583 & .566 & .601 &  .723 & .626 & .609 & .644 \\
Centrality             &  .655 & .577 & .573 & .581 &  .717 & .639 & .625 & .653 \\
Email count            &  .632 & .566 & .555 & .577 &  .718 & .650 & .639 & .662 \\
N. years active        &  .608 & .569 & .555 & .584 &  .702 & .610 & .594 & .626 \\
Number of authors      &  .578 & .536 & .529 & .544 &  .697 & .631 & .621 & .641 \\
Proportion in top      &  .663 & .594 & .580 & .609 &  .728 & .634 & .614 & .655 \\
Draft count            &  .500 & .445 & .401 & .500 &  .696 & .630 & .624 & .636 \\
N. Areas               &  .634 & .572 & .557 & .588 &  .721 & .639 & .622 & .657 \\
N. Mailing lists       &  .634 & .570 & .557 & .584 &  .718 & .641 & .630 & .653 \\
Affiliations           &  .605 & .584 & .576 & .592 &  .708 & .626 & .609 & .643 \\
Topic entropy ($\eta$) &  .622 & .563 & .550 & .577 &  .715 & .642 & .628 & .657 \\
Text                   & - & - & -  & -  &  .681 & .624 & .622 & .627 \\
Text (S)               & - & - & -  & -  &  .667 & .598 & .593 & .614 \\
\midrule
All feats              &  .692 & .624 & .600 & .651 &  .744 & .645 & .625 & .666 \\
All feats (S)          &  .692 & .624 & .600 & .651 &  .726 &  .636 &  .627 &  .664 \\
\bottomrule
\end{tabular}
\caption{
  Results for predicting adoption. Each row presents the scores of a model
  using the corresponding feature group either alone ($\neg \mathit{TXT}$)
  or combined with the Text features ($\mathit{TXT}$). \emph{All feats}
  denotes all features except the text. Rows labeled with (S)  use the
  \emph{Text (S)} variant of the text features.
}
\label{tbl:res}
\end{table*}

@@

\input{tables-prev/imc-2021/lr_fsnone-trim.tex}
\input{tables-prev/imc-2021/lr_fsauc-trim.tex}

>>>>

\begin{figure}[t]
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/imc-2021/documents/day_counts_yearly.pdf}
  \caption{
    Days from first draft to RFC publication
  }
  \label{fig:rfcs_days_to_pub}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/imc-2021/documents/draft_counts_yearly.pdf}
  \caption{
    Number of drafts per RFC
  }
  \label{fig:drafts_year}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/imc-2021/documents/page_counts_yearly_dt.pdf}
  \caption{
    RFC page counts
  }
  \label{fig:pages_year}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/imc-2021/documents/update_obsolete_yearly_pct.pdf}
  \caption{
    RFCs that update or obsolete previous RFCs
  }
  \label{fig:updates_year}
\end{figure}

\begin{figure}[t]
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/imc-2021/documents/cite_counts_yearly.pdf}
  \caption{
    Number of citations to other Internet-Drafts and RFCs per RFC in each
    year.
  }
  \label{fig:citations_year}
\end{figure}

@@

\begin{figure}[t]
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/imc-2021/documents/keyword_usage_rate.pdf}
  \caption{
    Number of occurrences of normative language keywords per page in RFCs
    in each year.
  }
  \label{fig:keyword_usage_rates}
\end{figure}

@@

\input{tables-prev/tma-2023/top-rfcs-errata.tex}

@@

%..................................................................................................
\pb{Errata per RFC Area, Status, and Stream:}
Figure~\ref{fig:errata_per_rfc} shows a CDF of the number of errata filed,
per RFC, in each IETF area. Non-IETF RFCs, e.g., IRTF and independent stream
RFCs, and legacy IETF RFCs, are labelled as ``None''.  We confirm errata in
standards are common: of the 4,373 standards-track RFCs in our dataset,
32.7\% have attracted at least one erratum filing.  However, there are
three notable outliers:

\input{tables-prev/tma-2023/errata-stats-area.tex}

\begin{enumerate}
  \item RFCs published by the Sub-IP (subip) Area have very few errata,
    with only 5\% of subip RFCs attracting errata filings. This temporary
    area -- established in 2001 and concluded in 2005 -- only published 19
    RFCs, resulting in a far smaller sample than the other areas. For
    comparison, the next smallest area, General (gen), published 39 RFCs.
    \emph{gen} RFCs attract a greater number of errata on average, vs.
    \emph{subip} RFCs, likely due to their broader relevance.

@@

In this section, we look at the authorship of published RFCs to explore
how participation in the IETF has changed over time. We show that the
geographic distribution of RFC authors has shifted over time, with the
proportion of authors from the US decreasing and a corresponding rise in
authors from Europe and China (\S\ref{sec:trends-demographics:geographic}).
We similarly explore shifts in affiliation, showing increasing influence of
Huawei and ongoing shifts in the fortunes of many prominent US and European
technology companies (\S\ref{sec:trends-demographics:affiliation}). 
% The ongoing influence of Cisco and strong input from academic institutions
% is also noted.

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/imc-2021/authors/top5_countries_normalised.pdf}
  \caption{
    Authorship countries (normalised)
  }
  \label{fig:author_countries_normalised}
\end{figure}

\begin{figure}[t!]
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/imc-2021/authors/continents_normalised.pdf}
  \caption{
    Authorship continents (normalised)
  }
  \label{fig:author_continents_normalised}
\end{figure}

@@

To measure influence of participants in the IETF we extend the analysis in
Section \ref{sec:org-dyn:participants} and, for each year, build a social
graph based on the \emph{active community} of participants who have
email interactions with any other participant in the previous five
years.

@@

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/icwsm-2022/lineplot_proportion_emailscount_top_percentile.pdf}
  \caption{
    Proportion of emails sent (\%) by participants in each period (with
    95\% confidence interval) according to their betweenness-centrality
    percentile (x-axis).  Y2-axis (purple) shows yearly count of emails.
  }
  \label{fig:emailcount_top_percentile}
\end{figure}

\begin{figure}[t!]
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/icwsm-2022/lineplot_avg_areas_top_percentile.pdf}
  \caption{
    Mean number of areas participated in (with 95\% confidence interval)
    according to their betweenness-centrality percentile in the x-axis,
    ranked from top (0-10) to bottom percentile (91-100).
  }
  \label{fig:areas_participation_top_percentile}
\end{figure}

\begin{figure}[t!]
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/icwsm-2022/lineplot_age_top_percentile.pdf}
  \caption{
    Mean participation duration (with 95\% confidence interval) according
    to their betweenness-centrality percentile in the x-axis, ranked from
    top (0-10) to bottom percentile (91-100).
  }
  \label{fig:age_top_percentile}
\end{figure}

@@

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/icwsm-2022/new_influencers_top10_age_longevityInTop10.pdf}
  \caption{
    Percentage of new influential participants breaking into top 10\%
    influencers (black); the average years of participation before entering
    top 10\% (purple); and minimum \#  years new influencers remain in top
    10\% (with 95\% confidence intervals).
  }
  \label{fig:rate_new_influential_participants}
\end{figure}

@@

Each topic is a distribution over words. For example, a \emph{security}
topic might have high probability for \emph{cypher}, \emph{rsa},
\emph{auth}, and related words. We can also use the model to obtain a
vector for any input text as a sparse distribution over all topics, e.g.,
finding that a text is comprised of 30\% security and 70\% video streaming
topics. With this, we generate a vector for each participant in a given
time period by concatenating all messages sent by that participant in the
period and feeding it into the LDA model. The result can be 
interpreted as a distribution of topics for each participant.

@@

We next measure diversity of a participant via the entropy of their topic
vector, their \emph{topic entropy}, defined as follows:
\begin{equation}
  \eta = - \sum_{i=1}^{|T|} p_i \log p_i \nonumber
\end{equation}
where $T = [p_1, ..., p_N]$ is a topic vector, which defines a probability
distribution over $N$ topics, each $p_i$ is a probability of the $i$-th
topic and $\sum_i p_i = 1$.

@@

@@

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/icwsm-2022/coauthor_affiliation_network/lineplot_non_overlapping_authors_emailnetwork_percentile.pdf}
  \caption{
    Percentage of Top 20\% authors that are not 20\% influencers according
    to their betweenness-centrality (email graph) percentile in the x-axis,
    ranked from  top (0-10) to bottom percentile (91-100).
  }
  \label{fig:non_overlapping_coauthornetwork_authors_emailnetwork}
\end{figure}

\begin{figure}[t!]
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/icwsm-2022/WG_chair_percentile_CDF_before_after.pdf}
  \caption{
    CDF of the percentile of betweenness-centrality of WG chairs in the
    email and co-authorship graph, one year before and after becoming
    chairs.
  }
  \label{fig:wg_chair_before_after}
\end{figure}

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/icwsm-2022/coauthor_affiliation_network/2019_affiliations_in_otheryears_coauthor_network.pdf}
  \caption{
    Authors in the most common affiliations of top 20\% authors
    (co-authorship graph) in 2015-2019.
  }
  \label{fig:coauthor_affiliation_network2019_otheryears}
\end{figure}

\begin{figure}[t!]
  \centering
  \includegraphics[width=\figureWidthOneColumn]{figures-prev/icwsm-2022/coauthor_affiliation_network/heatmap_2019_top10_affiliation_collaboration.pdf}
  \caption{
    Number of drafts co-authored by top 15 most frequently affiliated
    organisations. We only include the top 20\% authors (co-authorship
    graph) of 2015-2019.
  }
  \label{fig:heatmap_2019_coauthordraft_most_frequent_org}
\end{figure}

@@

For instance, if those in leadership positions send lots of email while
receiving little, this suggests a lack of receptiveness of the leadership
to the suggestions from regular participants, and low confidence of those
regular participants to voice their opinions. In contrast, 
if the IETF operates as outlined in its mission statement, in a more
cooperative manner, then communication between those in different roles
will be more symmetric.

@@

\begin{figure*}[t!]
  \centering
  \includegraphics[width=\figureWidthTwoColumn]{figures-prev/icwsm-2024/motif_strata_comparison.png}
  \caption{
    Communication patterns analysed by three edge temporal motifs for RPs,
  }
  \label{fig:motif_proportions}
\end{figure*}

\pb{Impact of Role on Communication Patterns:}
To quantify the effect being in a leadership position has on network
wide communication, we calculate the proportion of three node temporal
motifs, lasting at most a month, in which each node participates over a
year period. These temporal motifs are counted, categorised into
hierarchy levels (regular participant, working group chair, area director)
and then proportions are taken of each temporal motif.

@@

The larger proportion of those in leadership roles in Inward and Mixed Star
temporal motifs, whilst Outward Star motifs remain similar for all levels,
suggests that those in leadership receive more direct communication. The
higher proportion of Triangle motifs for regular participants suggests
their discussion is more of a group activity, whereas working group chairs
and area directors have a larger proportion of one-on-one conversations.  
We therefore interpret the general communication patterns within the IETF
as a discussion amongst participants interspersed with questions sent to,
and announcements from, the working group chairs and area directors.  This
indicates collaboration between layers and confidence of regular
participants' to voice their opinions upwards.

@@

\begin{figure*}[t!]
  \centering
  \includegraphics[width=\figureWidthTwoColumn]{figures-prev/icwsm-2024/hierarchy_status_comparison.png}
  \caption{
    Connection between roles and activity for regular participants and
    working group chairs viewed in terms of a) Mobility b) Neighbour
    Mobility c) Philanthropy and d) Community over time.
  }
  \label{fig:mob_tax}
\end{figure*}

@@

@@

\begin{figure*}[t!]
  \centering
  \includegraphics[width=\figureWidthTwoColumn]{figures-prev/frontiers/sensitive.pdf}
  \caption{
    Patterns of language use by organizational role. Estimated marginal
    means for the LIWC categories: (A) Politics, (B) Ethnicity, and (C)
    Religion. Error bars show 95% confidence intervals.
  }
  \label{fig:sensitive}
\end{figure*}

@@

@@

\renewcommand{\tabcolsep}{0.5cm}
\begin{table*}[t!]
\centering
\begin{tabular}{lcccccccc}
\toprule
                        & \multicolumn{4}{c}{$\neg \mathit{TXT}$}
                        & \multicolumn{4}{c} {$\mathit{TXT}$} \\
\midrule
                       & AUC & F1 & P & R & AUC & F1 & P & R \\
\midrule
Baseline               &  .500 & .445 & .401 & .500  &  .500 & .445 & .401 & .500 \\
\midrule
Comm. patterns         &  .644 & .583 & .566 & .601 &  .723 & .626 & .609 & .644 \\
Centrality             &  .655 & .577 & .573 & .581 &  .717 & .639 & .625 & .653 \\
Email count            &  .632 & .566 & .555 & .577 &  .718 & .650 & .639 & .662 \\
N. years active        &  .608 & .569 & .555 & .584 &  .702 & .610 & .594 & .626 \\
Number of authors      &  .578 & .536 & .529 & .544 &  .697 & .631 & .621 & .641 \\
Proportion in top      &  .663 & .594 & .580 & .609 &  .728 & .634 & .614 & .655 \\
Draft count            &  .500 & .445 & .401 & .500 &  .696 & .630 & .624 & .636 \\
N. Areas               &  .634 & .572 & .557 & .588 &  .721 & .639 & .622 & .657 \\
N. Mailing lists       &  .634 & .570 & .557 & .584 &  .718 & .641 & .630 & .653 \\
Affiliations           &  .605 & .584 & .576 & .592 &  .708 & .626 & .609 & .643 \\
Topic entropy ($\eta$) &  .622 & .563 & .550 & .577 &  .715 & .642 & .628 & .657 \\
Text                   & - & - & -  & -  &  .681 & .624 & .622 & .627 \\
Text (S)               & - & - & -  & -  &  .667 & .598 & .593 & .614 \\
\midrule
All feats              &  .692 & .624 & .600 & .651 &  .744 & .645 & .625 & .666 \\
All feats (S)          &  .692 & .624 & .600 & .651 &  .726 &  .636 &  .627 &  .664 \\
\bottomrule
\end{tabular}
\caption{
  Results for predicting adoption. Each row presents the scores of a model
  using the corresponding feature group either alone ($\neg \mathit{TXT}$)
  or combined with the Text features ($\mathit{TXT}$). \emph{All feats}
  denotes all features except the text. Rows labeled with (S)  use the
  \emph{Text (S)} variant of the text features.
}
\label{tbl:res}
\end{table*}

@@

@@

\renewcommand{\tabcolsep}{0.2cm}
\input{tables-prev/imc-2021/lr_fsnone-trim.tex}
\input{tables-prev/imc-2021/lr_fsauc-trim.tex}
